### 2021-04-15 Sleep Review Paper v1.Rmd
Updates

# Set working directory
setwd("~/Sleep Review")

# Download scoring sheet 
data.original <- read_excel("Sleep Review Scoring Sheet Test.xlsx")
```

>>>>

# Set working directory
setwd("~/Projects/sleep_circadian_demographics_data")

# Download scoring sheet 
data.original <- read_excel("scoring_rhiannon.xlsx")
```
